\documentclass[a4paper]{article}

% Import some useful packages
\usepackage[margin=0.5in]{geometry} % narrow margins
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{hyperref}
\usepackage{minted}
\usepackage{amsmath}
\usepackage{xcolor}
\definecolor{LightGray}{gray}{0.95}

\title{Peer-review of assignment 4 for \textit{INF3331-matan}}
\author{Reviewer 1, sebastps, {sebastps@student.matnat.uio.no} \\
 		Reviewer 2, andernev, {andernev@student.matnat.uio.no} \\
        We are one reviewer less, so we corrected one assignment less}
\begin{document}
\maketitle

\section{Review \emph{}}\label{sec:review}

Python 3.6.1 on macOS Sierra(version 10.12.6) is used for the review.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{General feedback}

This is a very good solution, well documented and everything we have tested is working. Very detailed and informative reports. Everything is easy to read, with good function names etc.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Assignment 4.1}

The tests have meaningful names, and is working as expected.
All the tests starter with test\_.
The code is very easy to read and also written in a pythonic way. No unnecessarily complicated parts.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Assignment 4.2} \label{sec:assignment5.2}

Working as expected and documentation where its needed.
Easy to read aswell.

\begin{minted}[bgcolor=LightGray, linenos, fontsize=\footnotesize]{python}
def integrate(f, a, b, N):
    """
    Integration method that does not use any python modules (numpy)
    """
    n = (b-a)/float(N) #Interval length
    I = 0.0 # Will be value of integrated function
    m = 0 # Counter
    for i in range(1, int(N)):
        m += 1
        I += f(a + i*n)*n
    I += f(b)*n
    return I
\end{minted}

The only thing i see is that the "m" counter here is not doing anything


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Assignment 4.3}

Working as expected and documentation where its needed.
Easy to read.
Numpy is used effectively. (Use of vectorization)
Good informative report

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Assignment 4.4}

Working as expected and documentation where its needed.
Easy to read. Good informative report. Good that you included the part about vectorized functions not working in numba.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Assignment 4.6}

Working as expected and documentation where its needed.
Easy to read. Good and informative report.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Assignment 4.7}
Packaging is done correctly

\subsection*{Assignment 4.8}
Bonus contest not done.

\bibliographystyle{plain}
\bibliography{literature}

\end{document}